---
title: "CNS_Final"
author: "Daniel Riddick"
date: "2022-11-15"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Libraries
```{r}
#Libraries
library(bibliometrix)
library(tidyverse)
```
Final Data Entry
```{r}
#Data input from 3 different keywords (keywords are specific research areas of interest within CNS that were attained through an interview process with personnel. The keywords list reflects a majority of research subject areas of interest.)

#First Keyword, Theoretical Physics with 4 bibtex files since WoS (Web of Science) only allows 500 publications extracted at one time.

Theo1 <- convert2df(file = 'C://Users//danie//Desktop//Theoretical_Physics//savedrecs.bib', dbsource = "wos", format = "bibtex")
Theo2 <- convert2df(file = 'C://Users//danie//Desktop//Theoretical_Physics//savedrecs2.bib', dbsource = "wos", format = "bibtex")
Theo3 <- convert2df(file = 'C://Users//danie//Desktop//Theoretical_Physics//savedrecs3.bib', dbsource = "wos", format = "bibtex")
Theo4 <- convert2df(file = 'C://Users//danie//Desktop//Theoretical_Physics//savedrecs4.bib', dbsource = "wos", format = "bibtex")
#Rbind, first there has to be all the same amount of columns
s <- which(colnames(Theo1) %in% colnames(Theo3))
Theo1 <- Theo1[,s]
s <- which(colnames(Theo2) %in% colnames(Theo3))
Theo2 <- Theo2[,s]
#Now Rbind all columns into one dataframe
Theo <- rbind(Theo1,Theo2)
Theo <- rbind(Theo,Theo3)
Theo <- rbind(Theo, Theo4)
#Deleting to clean up environment
Theo1 <- NULL; Theo2 <- NULL; Theo3 <- NULL; Theo4 <- NULL

#Second Keyword is Nuclear Engineering, remember that file paths are subject to change and that data must be aquired first from web of science

Nuc_Engin1 <- convert2df(file = 'C://Users//danie//Desktop//Nuclear_Engineering//savedrecs.bib', dbsource = "wos", format = "bibtex")
Nuc_Engin2 <- convert2df(file = 'C://Users//danie//Desktop//Nuclear_Engineering//savedrecs2.bib', dbsource = "wos", format = "bibtex")
Nuc_Engin3 <- convert2df(file = 'C://Users//danie//Desktop//Nuclear_Engineering//savedrecs3.bib', dbsource = "wos", format = "bibtex")
#Rbind, first there has to be all the same number of columns
s <- which(colnames(Nuc_Engin1) %in% colnames(Nuc_Engin3))
Nuc_Engin1 <- Nuc_Engin1[,s]
s <- which(colnames(Nuc_Engin2) %in% colnames(Nuc_Engin3))
Nuc_Engin2 <- Nuc_Engin2[,s]
#Now Rbind
Nuc_Engin <- rbind(Nuc_Engin1,Nuc_Engin2)
Nuc_Engin <- rbind(Nuc_Engin,Nuc_Engin3)
#Clean
Nuc_Engin1 <- NULL; Nuc_Engin2 <- NULL; Nuc_Engin3 <- NULL

#Last Keyword is Nonproliferation, it had under 500 publications after initial filters were utilized in web of science.

Nonproliferation <- convert2df(file = 'C://Users//danie//Desktop//Nonproliferation//savedrecs.bib', dbsource = "wos", format = "bibtex")

#Added due to errors for plots within Nonproliferation
Explosives_Engineering <- convert2df(file = 'C://Users//danie//Desktop//Nonproliferation//savedrecs2.bib', dbsource = "wos", format = "bibtex")


```
Data Validation, ROT Removal (Likely to be adjusted again in the future)

```{r}
#ROT Elimination (May need to be modified for bibliographic analysis)
#BO,earlyaccessdate,BE,eissn,BN,FX,organization,PP,researcherid.numbers,SE,AU_UN_NR
#Identified the numbers for each of the above listed columns as ROT
s <- which(colnames(Theo) %in% c('BO','earlyaccessdate','BE','eissn','BN','FX','organization','PP','researcherid.numbers','SE','AU_UN_NR'))
Theo <- Theo[,-s]

#Nuclear Engineering, c("note", "AU_UN_NR")
s <- which(colnames(Nuc_Engin)%in% c("note", "AU_UN_NR"))
Nuc_Engin <- Nuc_Engin[,-s]

#Nonproliferation, c("book.author","BO","BE","BN","note","oa","researcherid.numbers","SE","AU_UN_NR")
s <- which(colnames(Nonproliferation) %in% c("book.author","BO","BE","BN","note","oa","researcherid.numbers","SE","AU_UN_NR"))
Nonproliferation <- Nonproliferation[,-s]

#Added Explosives Engineering
s <- which(colnames(Explosives_Engineering) %in% c("book.author","BO","BE","BN","note","oa","researcherid.numbers","SE","AU_UN_NR"))
Explosives_Engineering <- Explosives_Engineering[,-s]
```

Rbind Merger Verification on Key Columns of Interest

```{r}
#Merger Verification by unique values for columns of interest for first keyword Theoretical Physics

#columns of interest, affiliations, SO(Journal name), TC (Times Cited), AU1_UN (Author affiliation)
#unique(Theo$affiliations) #its good but this code bogs down the computer
#unique(Theo$SO) #also good, also bogs down computer
#unique(Theo$TC) #Very good, important this is clean
#unique(Theo$AU1_UN) #Usable, some "Corresponding author mishaps, but overall fairly decent"

#Merger Verification by sampling unique values for columns of interest for second keyword Nuclear Engineering

#columns of interest, affiliations, SO(Journal name), TC (Times Cited), AU1_UN (Author affiliation)
#unique(Nuc_Engin$affiliations) #its good but this code bogs down the computer
#unique(Nuc_Engin$SO) #also good, also bogs down computer
#unique(Nuc_Engin$TC) #Very good, important this is clean
#unique(Nuc_Engin$AU1_UN) #Usable, some "Corresponding author mishaps, but overall fairly decent"

#Merger Verification by sampling unique values for columns of interest for third keyword Nonproliferation

#columns of interest, affiliations, SO(Journal name), TC (Times Cited), AU1_UN (Author affiliation)
#unique(Nonproliferation$affiliations) #its good 
#unique(Nonproliferation$SO) #also good
#unique(Nonproliferation$TC) #Very good, important this is clean
#unique(Nonproliferation$AU1_UN) #Usable
print("clean")
```
Sampling Method on Abstracts to ensure on target publication data

```{r}
#Sampling Method for abstracts to ensure they are on target, 10 per subject

#set.seed(1000);
#sample(Theo$AB, size = 10 , replace = F) #Consolidated, output heavy section (30 abstracts)
#Short topic notes for this iteration
#1. Physics of smooth trachea walls
#2. PDF of theoretical error, Red shifts, theoretical error
#3. Dimensional kinetic particle in-cell simulations
#4. Proton-Proton collisions results and comparisons to theoretical calculations
#5. Gravitational wave observations leading to modifications for general relativity
#6. Literature review that uses Quantum mechanics and other theoretical approaches? Not good
#7  The affect of pore fluids on acoustic wave dispersion in rocks
#8. Highly compressible pulsating flows
#9. SINGLE-MOLECULE DETECTION CAN REVEAL TIME TRAJECTORIES AND REACTION PATHWAYS OF INDIVIDUAL INTERMEDIATES/TRANSITION STATES IN CHEMICAL REACTIONS AND BIOLOGICAL PROCESSES
#10. Condensed matter physics, activated dynamics in diverse glass forming liquids.

#set.seed(1000);
#sample(Nuc_Engin$AB, size = 10 , replace = F)
#1. Mechanistic interpretation of clay dehydration being key to coupling natural/engineered barriers
#2. Prompt Gamma Activation Analysis to quantify Boron concentrations in Boron Carbide Semiconductor
#3. Graphite reactor components for reactor operator to arrive at optimum component replacement schedule for the graphite components to improve safety.
#4. Next generation nuclear plant using printed circuit heat exchangers, with super critical carbon dioxide SCO(2) as the working fluid
#5. Genetically engineered bacteria to help fight influenza (Virology off-target)
#6. Another advanced nuclear power plant
#7. More focused on Nonproliferation 
#8. seismic isolation systems to protect nuclear infrastructure
#9. Cost and usage of Nuclear density gauge
#10. Lessons of the Fukishima reactor incident

#set.seed(1000);
#sample(Nonproliferation$AB, size = 10, replace = F)
#1. Improved understanding of evolution of the nonproliferation regime through examining US and French Nuclear Cooperation agreements
#2. Chernobyl incident review
#3. Detecting, localizing, and characterizing nuclear material for safeguard and nonproliferation
#4. Complex ionization tests from Sandia in order to ultimately help medical physics, national security and nonproliferation.
#5. Sphere of A-phase plutonium subjected to passive imagining using optically stimulated luminescence 
#6. FOR THE FIRST TIME, THE NEUTRON AND GAMMA-RAY TIME-DEPENDENT CROSS-CORRELATION DISTRIBUTIONS FROM SPONTANEOUS FISSION AND (ALPHA, N) NEUTRON SOURCES ARE MEASURED WITH THE HE-4 FAST NEUTRON DETECTORS.
#7. NA
#8. "ROSSI-ALPHA NEUTRON EXPERIMENTS ARE USED TO ESTIMATE THE PROMPT NEUTRON DECAY CONSTANT OF A FISSILE ASSEMBLY, A QUANTITY OF WIDESPREAD INTEREST IN APPLICATIONS INCLUDING IN NUCLEAR NONPROLIFERATION AND CRITICALITY SAFETY.
#9. "MUCH OF INTERNATIONAL RELATIONS SCHOLARSHIP ATTRIBUTES THE UNITED STATES' COMMITMENT TO PREVENT THE GLOBAL SPREAD OF NUCLEAR WEAPONS AS THE OUTCOME OF US NATIONAL SECURITY INTERESTS.
#10. TO SUPPORT EFFORTS TO STEM THE PROLIFERATION OF CHEMICAL WEAPONS (CWS), WE HAVE CURATED AND STRUCTURALLY ANNOTATED CW-CONTROL LISTS FROM THREE KEY INTERNATIONAL NONPROLIFERATION FRAMEWORKS: THE CHEMICAL WEAPONS CONVENTION (CWC), THE AUSTRALIA GROUP (AG), AND THE WASSENAAR ARRANGEMENT.
print("clean")
```

Storing Publication Countries of Origin

```{r}
#Single Country Publications Only

#C1 is author address. Starting with Explosives Engineering
results <- biblioAnalysis(Explosives_Engineering) 
#plot(x = results) #Shows multiple country publications

#Determine a means of extracting countries of origin reliably using the C1 variable
#results$CO #This gives Countries
Explosives_Engineering$CO <- results$CO


#Now Theoretical Physics
results <- biblioAnalysis(Theo) 
#plot(x = results) #Shows multiple country publications

#results$CO #This gives Countries
Theo$CO <- results$CO


#Nuclear Engineering
results <- biblioAnalysis(Nuc_Engin) 
#plot(x = results) #Shows multiple country publications

#results$CO #This gives Countries
Nuc_Engin$CO <- results$CO


#Nonproliferation
results <- biblioAnalysis(Nonproliferation) 
#plot(x = results) #Plot does not work for nonproliferation

#results$CO #This gives Countries
Nonproliferation$CO <- results$CO
```

Removal of international publications and multiple country collaborations to ensure domestic collaboration.

```{r}
#Extract only Single country publications from the USA
Theo <- Theo[which(Theo$CO == "USA"),]
Nuc_Engin <- Nuc_Engin[which(Nuc_Engin$CO == "USA"),]
Nonproliferation <- Nonproliferation[which(Nonproliferation$CO == "USA"),]
Explosives_Engineering <- Explosives_Engineering[which(Explosives_Engineering$CO == "USA"),]
```

Binomial tests on n = 100 samples of keywords for each subject area, indicates a potential population accuarcy for on target publications.

```{r}
#Additional on target validation by keywords by gauging an on target list of keywords as a success and off target keywords as failures. Binomial test and 95% confidence interval are provided.

#Theoretical Physics
#set.seed(1000); sample(Theo$web.of.science.categories., size = 100, replace = F)
#12 keywords were off-target, giving an estimated proportion of 88/100 on target
binom.test(88,100)
#Given this sample, we can say that we are 95% confident the true proportion of on target publications for theoretical physics is between 0.7997643 and 0.9364311


#Nuclear Engineering
#set.seed(1000); sample(Nuc_Engin$web.of.science.categories., size = 100, replace = F)
#Nuclear engineering is a broad topic incorporating some medical advancements that deal with by definition, Nuclear Engineering, these are included as success.
#10 off-target publications, 90/100 successes
binom.test(90,100)
#Given this sample, we can say that we are 95% confident the true proportion of on target publications for Nuclear Engineering is between 0.8237774 and 0.9509953


#Nonproliferation
#set.seed(1000); sample(Nonproliferation$web.of.science.categories., size = 100, replace = F)
#5 keywords were off-target, giving an estimated proportion of 95/100 on target publications.
binom.test(95,100)
#Given this sample, we can say that we are 95% confident the true proportion of on target publications for Nonproliferation is between 0.8871651 and 0.9835681. However, it is important to note that it was assumed nonproliferation comes in forms of law, international relations, engineering practices, research, etc. Only obvious off-topic publications were counted as failures.

#Explosives Engineering
#Explosives_Engineering$web.of.science.categories.
#Do not know that much about explosives engineering, results may be neglected.
#Including forms of potential botany, engineering components, physics, material science, and chemistry. 
#9 off target, 63 successes
binom.test(63,72)
#Given this sample, we can say that we are 95% confident the true proportion of on target publications for Explosives Engineering is between 0.7759281 and 0.9412167.


```
Citation Count Adjustment for Adapted Pure H-Index, being used is adjusting the Times Cited variable as
 TC/sqrt("Number of Authors for a publication").

```{r}
#TC is times cited, adjustments made on TC will reflect in new H-index values. Adjustment decreases bias.
Explosives_Engineering$AU_Count <- (str_count(Explosives_Engineering$AU, ";")+1)
Explosives_Engineering$TC <- round(Explosives_Engineering$TC/sqrt(Explosives_Engineering$AU_Count))

Theo$AU_Count <- (str_count(Theo$AU, ";")+1)
Theo$TC <- round(Theo$TC/sqrt(Theo$AU_Count))

Nonproliferation$AU_Count <- (str_count(Nonproliferation$AU, ";")+1)
Nonproliferation$TC <- round(Nonproliferation$TC/sqrt(Nonproliferation$AU_Count))

Nuc_Engin$AU_Count <- (str_count(Nuc_Engin$AU, ";")+1)
Nuc_Engin$TC <- round(Nuc_Engin$TC/sqrt(Nuc_Engin$AU_Count))

```


Initial bibliometric analysis, consolidation of results using bibliometrix package function 

```{r}
#C1 is author address. Starting with Explosives Engineering
results_Exp_Eng <- biblioAnalysis(Explosives_Engineering) 
#plot(x = results) #Shows multiple country publications

#Determine a means of extracting countries of origin reliably using the C1 variable


#Now Theoretical Physics
results_Theo <- biblioAnalysis(Theo) 
#plot(x = results) #Shows multiple country publications



#Nuclear Engineering
results_Nuc_Engin <- biblioAnalysis(Nuc_Engin) 
#plot(x = results) #Shows multiple country publications


#Nonproliferation
results_Nonproliferation <- biblioAnalysis(Nonproliferation) 
#plot(x = results) #Plot does not work for nonproliferation


```

Affiliations Visualizations

```{r}

par(mar = c(7, 4, 2, 2) + 0.2); end_point = 0.5 + nrow(results_Nonproliferation$Affiliations[1:20]) + nrow(results_Nonproliferation$Affiliations[1:20]) - 1 ; barplot(results_Nonproliferation$Affiliations[1:20], col = "steelblue", 
        main = "Most Notable Affiliations for Nonproliferation",
        ylab = "Frequency of Publications", ylim = c(0,5 + max(results_Nonproliferation$Affiliations[1:20])),
        xlab = "",
        xaxt = "n", 
        space = 1);text(seq(1.5, end_point, by = 2), par("usr")[3]-0.25, 
     srt = 60, adj = 1, xpd = TRUE,
     labels = paste(rownames(results_Nonproliferation$Affiliations[1:20])), cex = 0.65)

```

```{r}
par(mar = c(7, 4, 2, 2) + 0.2); end_point = 0.5 + nrow(results_Exp_Eng$Affiliations[1:20]) + nrow(results_Exp_Eng$Affiliations[1:20]) - 1 ; barplot(results_Exp_Eng$Affiliations[1:20], col = "orangered", 
        main = "Most Notable Affiliations for Explosives Engineering",
        ylab = "Frequency of Publications", ylim = c(0,5 + max(results_Exp_Eng$Affiliations[1:20])),
        xlab = "",
        xaxt = "n", 
        space = 1);text(seq(1.5, end_point, by = 2), par("usr")[3]-0.25, 
     srt = 60, adj = 1, xpd = TRUE,
     labels = paste(rownames(results_Exp_Eng$Affiliations[1:20])), cex = 0.65)
```

```{r}
par(mar = c(7, 4, 2, 2) + 0.2); end_point = 0.5 + nrow(results_Nuc_Engin$Affiliations[1:20]) + nrow(results_Nuc_Engin$Affiliations[1:20]) - 1 ; barplot(results_Nuc_Engin$Affiliations[1:20], col = "yellowgreen", 
        main = "Most Notable Affiliations for Nuclear Engineering",
        ylab = "Frequency of Publications", ylim = c(0,5 + max(results_Nuc_Engin$Affiliations[1:20])),
        xlab = "",
        xaxt = "n", 
        space = 1);text(seq(1.5, end_point, by = 2), par("usr")[3]-0.25, 
     srt = 60, adj = 1, xpd = TRUE,
     labels = paste(rownames(results_Nuc_Engin$Affiliations[1:20])), cex = 0.65)
```

```{r}
par(mar = c(7, 4, 2, 2) + 0.2); end_point = 0.5 + nrow(results_Theo$Affiliations[1:20]) + nrow(results_Theo$Affiliations[1:20]) - 1 ; barplot(results_Theo$Affiliations[1:20], col = "brown", 
        main = "Most Notable Affiliations for Theoretical Physics",
        ylab = "Frequency of Publications", ylim = c(0,5 + max(results_Theo$Affiliations[1:20])),
        xlab = "",
        xaxt = "n", 
        space = 1);text(seq(1.5, end_point, by = 2), par("usr")[3]-0.25, 
     srt = 60, adj = 1, xpd = TRUE,
     labels = paste(rownames(results_Theo$Affiliations[1:20])), cex = 0.65)
```

Storing Local Citation Counts in Each Data Frame 
```{r}
#Creating a local citation count for each paper for original data set, this one is for Nonproliferation
results <- localCitations(Nonproliferation)
results$Papers <- results$Papers[order(results$Papers$Paper,decreasing = F),]
Nonproliferation <- Nonproliferation[order(rownames(Nonproliferation),decreasing = F),]
Nonproliferation$LocalCitations <- results$Papers$LCS


#Theoretical Physics
results <- localCitations(Theo)
results$Papers <- results$Papers[order(results$Papers$Paper,decreasing = F),]
Theo <- Theo[order(rownames(Theo),decreasing = F),]
Theo$LocalCitations <- results$Papers$LCS


#Nuclear Engineering
results <- localCitations(Nuc_Engin)
results$Papers <- results$Papers[order(results$Papers$Paper,decreasing = F),]
Nuc_Engin <- Nuc_Engin[order(rownames(Nuc_Engin),decreasing = F),]
Nuc_Engin$LocalCitations <- results$Papers$LCS


#Explosives Engineering
results <- localCitations(Explosives_Engineering)
results$Papers <- results$Papers[order(results$Papers$Paper,decreasing = F),]
Explosives_Engineering <- Explosives_Engineering[order(rownames(Explosives_Engineering),decreasing = F),]
Explosives_Engineering$LocalCitations <- results$Papers$LCS

```

Local Co-citation Network Analysis to determine novelty of specific publications (Issues with Explosive Engineering, unsure of cause) Plots show a historic overlook of local co-citation, indicating associated authors of interest and authors capable of novel research. Metrics attached with plot output.

```{r}

#Theoretical Physics
options(width=130)
histResults <- histNetwork(Theo, min.citations = 1, sep = ";")
net <- histPlot(histResults, n=length(Theo), size = 10, labelsize=3)


#Nuclear Engineering
options(width=130)
histResults <- histNetwork(Nuc_Engin, min.citations = 1, sep = ";")
net <- histPlot(histResults, n=length(Nuc_Engin), size = 10, labelsize=3)


#Explosives Engineering
#options(width=130)
#histResults <- histNetwork(Explosives_Engineering, min.citations = 1, sep = ";")
#net <- histPlot(histResults, n=length(Explosives_Engineering), size = 10, labelsize=3)


#Nonproliferation
options(width=130)
histResults <- histNetwork(Nonproliferation, min.citations = 1, sep = ";")
net <- histPlot(histResults, n=length(Nonproliferation), size = 10, labelsize=3)
```

Additional Potential Output (Dendograms, K-means clustering on common concepts within documents)

```{r}
A <- cocMatrix(Theo, Field = "CR", sep = ".  ")
A
sort(Matrix::colSums(A), decreasing = TRUE)[1:20]

CS <- conceptualStructure(Nonproliferation,field="ID", method="CA", minDegree=4, clust=5, stemming=FALSE, labelsize=10, documents=10)

CS <- conceptualStructure(Theo,field="ID", method="MCA", minDegree=4, clust=5, stemming=F, labelsize=10, documents=10)

CS <- conceptualStructure(Nuc_Engin,field="ID", method="CA", minDegree=4, clust=5, stemming=FALSE, labelsize=10, documents=10)
```


Top 10 Author results for adapted pure H-Index using a weighted novelty score. The more local citations a publication has, considering only publications in a 5 year span, indicate more novel research. This is combined with an adapted pure H-index by allowing for a weighted bonus for local citations within the data. Scroll on initial data frame to see output.

```{r}
#For Explosives Engineering, run entire chunk until "For Nonproliferation"
#Here code is for initial adapted pure H-index Calculation
authors <- gsub(","," ",names(results_Exp_Eng$Authors))
indices <- Hindex(Explosives_Engineering, field = "author", elements = authors, sep = ";", years = 20)
indices$H[order(indices$H$h_index, decreasing = T),]

#This is code is being used to find where authors are located in the large initial data frame so that authors of interest can be pulled out, along with their papers, email, abstracts of papers, affiliations, and keywords associated to the papers.
row_numbers_for_authors_Exp <- c()

for (i in 1:nrow(indices$H)) {
  
row_numbers_for_authors_Exp[i] <-  list(which(str_detect(Explosives_Engineering$AU, pattern = indices$H$Element[i])))

}
#This is the connection to the large initial data frame and the H-index data frame.
indices$H$row <- row_numbers_for_authors_Exp
indices$H <- indices$H[order(indices$H$h_index, decreasing = T),]
Explosives_Engineering[unlist(indices$H$row[1:10]),] %>% select(c("AU", "EM", "affiliations","ID" ,"AB","LocalCitations"))



#For Nonproliferation
authors <- gsub(","," ",names(results_Nonproliferation$Authors))
indices <- Hindex(Nonproliferation, field = "author", elements = authors, sep = ";", years = 20)
indices$H[order(indices$H$h_index, decreasing = T),]

row_numbers_for_authors_Exp <- c()

for (i in 1:nrow(indices$H)) {
  
row_numbers_for_authors_Exp[i] <-  list(which(str_detect(Nonproliferation$AU, pattern = indices$H$Element[i])))

}
indices$H$row <- row_numbers_for_authors_Exp
indices$H <- indices$H[order(indices$H$h_index, decreasing = T),]
Nonproliferation[unlist(indices$H$row[1:10]),] %>% select(c("AU", "EM", "affiliations","ID" ,"AB",'LocalCitations'))


#For Nuclear Engineering
authors <- gsub(","," ",names(results_Nuc_Engin$Authors))
indices <- Hindex(Nuc_Engin, field = "author", elements = authors, sep = ";", years = 20)
indices$H[order(indices$H$h_index, decreasing = T),]

row_numbers_for_authors_Exp <- c()

for (i in 1:nrow(indices$H)) {
  
row_numbers_for_authors_Exp[i] <-  list(which(str_detect(Nuc_Engin$AU, pattern = indices$H$Element[i])))

}
indices$H$row <- row_numbers_for_authors_Exp
indices$H <- indices$H[order(indices$H$h_index, decreasing = T),]
Nuc_Engin[unlist(indices$H$row[1:10]),] %>% select(c("AU", "EM", "affiliations","ID" ,"AB","LocalCitations"))



#For Theoretical Physics
authors <- gsub(","," ",names(results_Theo$Authors))
indices <- Hindex(Theo, field = "author", elements = authors, sep = ";", years = 20)
indices$H[order(indices$H$h_index, decreasing = T),]

row_numbers_for_authors_Exp <- c()

for (i in 1:nrow(indices$H)) {
  
row_numbers_for_authors_Exp[i] <-  list(which(str_detect(Theo$AU, pattern = indices$H$Element[i])))

}

indices$H$row <- row_numbers_for_authors_Exp
indices$H <- indices$H[order(indices$H$h_index, decreasing = T),]
Theo[unlist(indices$H$row[1:10]),] %>% select(c("AU", "EM", "affiliations","ID" ,"AB", "LocalCitations"))
```

Lotkas Law Coefficient, measures the expected frequency of authors and their number of publications vs. the observed frequency of authors and their number of publications.


```{r}
#Lotka Nonproliferation
L <- lotka(results_Nonproliferation)
L$AuthorProd
# Observed distribution
Observed=L$AuthorProd[,3]
# Theoretical distribution with Beta = 2
Theoretical=10^(log10(L$C)-2*log10(L$AuthorProd[,1]));plot(L$AuthorProd[,1],Theoretical,type="l",col="red",ylim=c(0, 1), xlab="Articles",ylab="Freq. of Authors",main="Scientific Productivity Nonproliferation");lines(L$AuthorProd[,1],Observed,col="blue");legend(x="topright",c("Theoretical (B=2)","Observed"),col=c("red","blue"),lty = c(1,1,1),cex=0.6,bty="n")

#Lotka Explosives Engineering
L <- lotka(results_Exp_Eng)
L$AuthorProd
# Observed distribution
Observed=L$AuthorProd[,3]
# Theoretical distribution with Beta = 2
Theoretical=10^(log10(L$C)-2*log10(L$AuthorProd[,1]));plot(L$AuthorProd[,1],Theoretical,type="l",col="red",ylim=c(0, 1), xlab="Articles",ylab="Freq. of Authors",main="Scientific Productivity Explosives Engineering");lines(L$AuthorProd[,1],Observed,col="blue");legend(x="topright",c("Theoretical (B=2)","Observed"),col=c("red","blue"),lty = c(1,1,1),cex=0.6,bty="n")

#Lotka Nuclear Engineering
L <- lotka(results_Nuc_Engin)
L$AuthorProd
# Observed distribution
Observed=L$AuthorProd[,3]
# Theoretical distribution with Beta = 2
Theoretical=10^(log10(L$C)-2*log10(L$AuthorProd[,1]));plot(L$AuthorProd[,1],Theoretical,type="l",col="red",ylim=c(0, 1), xlab="Articles",ylab="Freq. of Authors",main="Scientific Productivity Nuclear Engineering");lines(L$AuthorProd[,1],Observed,col="blue");legend(x="topright",c("Theoretical (B=2)","Observed"),col=c("red","blue"),lty = c(1,1,1),cex=0.6,bty="n")

#Lotka Theoretical Physics
L <- lotka(results_Theo)
L$AuthorProd
# Observed distribution
Observed=L$AuthorProd[,3]
# Theoretical distribution with Beta = 2
Theoretical=10^(log10(L$C)-2*log10(L$AuthorProd[,1]));plot(L$AuthorProd[,1],Theoretical,type="l",col="red",ylim=c(0, 1), xlab="Articles",ylab="Freq. of Authors",main="Scientific Productivity Theoretical Physics");lines(L$AuthorProd[,1],Observed,col="blue");legend(x="topright",c("Theoretical (B=2)","Observed"),col=c("red","blue"),lty = c(1,1,1),cex=0.6,bty="n")
```

(CSV Extract for Final Data)

```{r}
write.csv(Theo, file = "C:\\Users\\danie\\Desktop\\Web of Science Data\\Theo.csv")
write.csv(Nuc_Engin, file = "C:\\Users\\danie\\Desktop\\Web of Science Data\\Nuc_Engin.csv")
write.csv(Nonproliferation, file = "C:\\Users\\danie\\Desktop\\Web of Science Data\\Nonproliferation.csv")
write.csv(Explosives_Engineering, file = "C:\\Users\\danie\\Desktop\\Web of Science Data\\Explosives_Engineering.csv")
```



